### 2020-03-18 AlgebraicTopology2020/algtop3/algtop3.tex
Update algtop3 & fix \Cat spacing

	\begin{enumerate}
	\item By definition, we have:
	\begin{equation}
	\begin{tikzcd}[row sep=8.5ex,column sep=7ex]
		& \Delta(\lim F)
			\arrow[d,Rightarrow,"\sigma"] \\
		\Delta(V)
			\arrow[r,Rightarrow,"\eta"]
			\arrow[ur,Rightarrow,dashed,%
				"\exists!\,\Delta(g)"] &
		F
	\end{tikzcd}
	\label{eq:def_limit}
	\end{equation}
	Where $g\colon V\to \lim F$. 
	More intuitively, for the above $F\colon I\to\Cat{Vect}$, this translates to the following diagram in \Cat{Vect}:
	\begin{equation}
	\begin{tikzcd}[row sep=2ex,column sep=8ex]
		&& 0 \\
		V
			\arrow[r,dashed,
				"\exists!\, g"]
			\arrow[urr,bend left,%
				"\eta_\bullet"]
			\arrow[drr,bend right,swap,%
				"\eta_\star"] &
		\lim F
			\arrow[ur,%
				"\sigma_\bullet"]
			\arrow[dr,swap,%
				"\sigma_\star"] & \\
		&& \mbb{R}
	\end{tikzcd}
	\label{eq:lim_in_vect}
	\end{equation}
	\end{enumerate}

@@

	On the other hand, $\colim F$ is the ``largest'' object that any map \textit{out of} $\Zpoly{n}$ must ``passes through''. Also, this should hold for all $n\in\mbb{Z}_+$. Naturally, projections $
		\sigma_n\colon\Zpoly{n}\to\mbb{Z}
	$ satisfy the above requirements; we have:
	\begin{gather}
		\sigma_n\colon\ x\longmapsto 0,\quad
			\sum_{m=0}^{n-1} a_m x^m
			\longmapsto a_0,\\
		\sigma_{n+1}
		= p_1\circ p_2\circ\cdots p_n
	\end{gather}
	$g\colon \mbb{Z}\to R$ in \eqref{eq:polynomial_ring_tower} is fixed uniquely for such choice of $\sigma_n$; in fact, descend along the $p_n$ tower in \eqref{eq:polynomial_ring_tower}, and we have: $
		\tau_{n+1}
		= \tau_n\circ p_n
		= \tau_{n-1}\circ p_{n-1}\circ p_n
		= \cdots
		= \tau_1\circ p_1\circ p_2\circ\cdots p_n
		= \tau_1\circ \sigma_{n+1},
		\ \forall\ n\in\mbb{Z}_+
	$, hence $\exists\,!\ g = \tau_1$. Therefore, $\colim F = \mbb{Z}$. \qed

>>>>

	\begin{enumerate}
	\item By definition, we have:
	\begin{equation}
	\begin{tikzcd}[row sep=8.5ex,column sep=5ex]
		& \Delta(\lim F)
			\arrow[d,Rightarrow,"\sigma"] \\
		\Delta(V)
			\arrow[r,Rightarrow,"\eta"]
			\arrow[ur,Rightarrow,dashed,%
				"\exists!\,\Delta(g)"] &
		F
	\end{tikzcd}
	\label{eq:def_limit}
	\end{equation}
	Where $g\colon V\to \lim F$. 
	More intuitively, for the above $F\colon I\to\Cat{Vect}$, this translates to the following diagram in \Cat{Vect}:
	\begin{equation}
	\begin{tikzcd}[row sep=2ex,column sep=8ex]
		&& 0 \\
		V
			\arrow[r,dashed,
				"\exists!\, g"]
			\arrow[urr,bend left,%
				"\eta_\bullet"]
			\arrow[drr,bend right,swap,%
				"\eta_\star"] &
		\lim F
			\arrow[ur,%
				"\sigma_\bullet"]
			\arrow[dr,swap,%
				"\sigma_\star"] & \\
		&& \mbb{R}
	\end{tikzcd}
	\label{eq:lim_in_vect}
	\end{equation}
	\end{enumerate}

@@

	On the other hand, $\colim F$ is the ``largest'' object that any map \textit{out of} $\Zpoly{n}$ must ``passes through''. Also, this should hold for all $n\in\mbb{Z}_+$. Naturally, projections $
		\sigma_n\colon\Zpoly{n}\to\mbb{Z}
	$ satisfy the above requirements; we have:
	\begin{gather}
		\sigma_n\colon\ x\longmapsto 0,\quad
			\sum_{m=0}^{n-1} a_m x^m
			\longmapsto a_0,\\
		\sigma_{n+1}
		= p_1\circ p_2\circ\cdots p_n
	\end{gather}
	$g\colon \mbb{Z}\to R$ in \eqref{eq:polynomial_ring_tower} is fixed uniquely for such choice of $\sigma_n$; in fact, descend along the $p_n$ tower in \eqref{eq:polynomial_ring_tower}, and we have: $
		\tau_{n+1}
		= \tau_n\circ p_n
		= \tau_{n-1}\circ p_{n-1}\circ p_n
		= \cdots
		= \tau_1\circ p_1\circ p_2\circ\cdots p_n
		= \tau_1\circ \sigma_{n+1},
		\ \forall\ n\in\mbb{Z}_+
	$, hence $\exists\,!\ g = \tau_1$. Therefore, $\colim F = \mbb{Z}$. \qedfull

	\item \textbf{Example of push-out in \Cat{Groupoid}:}
	\begin{equation}
	\begin{tikzcd}[row sep=8.5ex,column sep=6.5ex]
		\{0,1\}
			\arrow[r,"f_1"]
			\arrow[d,"f_2",swap] &
		\bullet
			\arrow[d,"\tau_1"]
			\arrow[ddr,bend left,"\eta_1"] &[1ex] \\
		\{ 0\leftrightarrow 1 \}
			\arrow[r,"\tau_2"]
			\arrow[drr,bend right,"\eta_2"] &
		P
			\arrow[dr,dotted
				,"\!\!\exists!\,g" description]
		& \\[-2.5ex]
		&& Q
	\end{tikzcd}
	\end{equation}

	Following the same observation as before, the push-out $P$ is the ``largest'' object that any map out of $\bullet$ and $\{0\leftrightarrow  1\}$ must pass through. By such universal property, $P$ can be no larger than the coproduct: $
		\{\bullet\} \coprod \{0\leftrightarrow 1\}
	$. However, we should also consider the equivalence imposed by: 
	\begin{equation}
		\bullet
		\xlongleftarrow{\ f_1\,} \{0,1\}
		\xlongrightarrow{\ f_2\ }
		\{0\leftrightarrow 1\}
	\end{equation}
	Therefore, we simply have $P = \bullet$, with $\tau_{1,2}$ the natural projection. This can be verified with ease: we have $g = \eta_1$. It is unique since its image is a single point (with identity map to itself) $\star \in Q$, and the point $\star$ is fixed by commutativity. \qedfull

	\item \textbf{Product and coproduct in \Cat{Ab}:}

	For $G_\alpha\in\Cat{Ab}\subset\Cat{Group}$, note that we have:
	\begin{equation}
		\mop{Free}:
			\Cat{Set}
			\xrightleftharpoons{\quad}
			\Cat{Group}
		:\mop{Forget}
	\label{eq:free_forget_adjoint}
	\end{equation}
	Therefore, for $F$: some diagram in \Cat{Group}, $
		\boxed{\lim\,(\mop{Forget}\circ F)
		= \mop{Forget}\circ\lim F}
	$ if $\lim F$ exists.

	By definition, the product $\prod_\alpha G_\alpha\in \Cat{Group}$ is a limit, hence it is idential (as in $\Cat{Set}\mspace{.2mu}$) to the \textit{direct product}, with additional entry-wise group multiplication. Same applies for the full subcategory: abelian group $\Cat{Ab}\subset\Cat{Group}$.

	On the other hand, the disjoint union of $G_\alpha$'s as sets will not necessary be a group, the identities $\idty_\alpha\in G_\alpha$ must be glued together to produce a group structure. Furthermore, free-forgetful adjunction \eqref{eq:free_forget_adjoint} implies that for $F'$: some diagram in \Cat{Set},
	\begin{equation}
		\colim\,(\mop{Free}\circ F')
		= \mop{Free}\circ\colim F',\quad
	\end{equation}
	Whenever $\colim F'$ exists; in our case, $\colim F'$ is the disjoint union of sets: $
		\coprod_\alpha \mop{Forget}(G_\alpha)
	$. Therefore, we should construct a free object in \Cat{Ab}.

	Here we restrict our discussion to \Cat{Ab}, since the coproduct in $\Cat{Ab}$ is \textit{not} the same as in $\Cat{Group}$ --- the free product of abelian group is not necessary abelian. Hence, the coproduct in \Cat{Ab} shall be:
	\begin{equation}
		\coprod_\alpha G_\alpha
		= \bigoplus_\alpha G_\alpha,\quad
		i_\alpha\colon\, G_\alpha
			\ \xhookrightarrow{\quad}\ %
			\bigoplus_\alpha G_\alpha
	\end{equation}
	As a set, this is precisely the disjoint union with identities $0_\alpha \in G_\alpha \subset \Cat{Ab}$ glued together.

	It is then straight-forward to verify its universal property: for $f_\alpha\colon G_\alpha\to H$,
	\begin{equation}
		\exists\,!\ f\colon\,%
			\bigoplus_\alpha G_\alpha
			\ \longto\ H,\quad
		(g_\alpha)_\alpha
			\ \longmapsto\ %
			\sum_\alpha f_\alpha(g_\alpha)
	\end{equation}
	This is compatible with the abelian group multiplication. Note that for the summation to be well-defined, the coproduct must only contain finitely many components; otherwise it is identical to the product in \Cat{Ab}. 
	\qedfull
